---
title: "Week 01 Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Exercises

1.  Explain coercion rules. Create an example that demonstrates the fixed order of the coercion rules.

```{r}

```

2.  The following code will generate a warning. Explain why.

```{r}
as.integer(c("one", "two", "three"))
```

3.  Create a vector of a sequence of integers starting at 2, ending at 100, and increasing by 2. Assign the vector to an object called `evens`. Coerce the vector to be of type `integer`. Confirm that the vector is of type `integer`.

```{r}

```

4.  Create a vector of random numbers with a length equal to your vector in exercise 3. Use a seed with a value of 730 before creating your vector. Assign the vector to an object called `randoms`. Confirm the type of the vector.

```{r}

```

5.  Create a vector demonstrating which values in exercise 3 are greater than `0.75`. Assign the vector to an object called `logicals`. Confirm the type of the vector.

```{r}

```

6.  Create a data frame including the three vectors created in exercises 3 through 5. Assign it to an object following best practices for naming.

```{r}

```

7.  Create a new object which is the sum of `evens` and `randoms` all divided by 3. Demonstrate how to calculate basic summary statistics for this new object (mean, median, minimum, maximum, standard deviation, variance).

```{r}

```

8.  We discussed the idea that R is a "vectorized" language. Explain this concept. Why is it important?

9.  Run the `sessionInfo` function in a chunk.

```{r}

```
