---
title: "Week 01 Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This assignment is meant to reinforce our learnings from the first week of class while also providing additional background and support for using git.

We will be using GitHub for submitting assignments. We will review assignment submission during our second class. You will submit this assignment at that time.

#### Textbook

-   Review from this past week:
    -   [Chapter 2 - Explore Introduction](https://r4ds.had.co.nz/explore-intro.html)
    -   [Chapter 4 - Workflow Basics](https://r4ds.had.co.nz/workflow-basics.html)
    -   [Chapter 6 - Workflow: scripts](https://r4ds.had.co.nz/workflow-scripts.html)

-   Prepare for next week:
    -   [Chapter 3 - Data visualization](https://r4ds.had.co.nz/data-visualisation.html)

#### Additional Readings

-   [*Happy Git and GitHub for the useR*](https://happygitwithr.com/)

    -   Chapter 1
    -   Chapters 4-7
    -   Chapters 9-14

#### Exercises

1.  Explain coercion rules. Create an example that demonstrates the fixed order of the coercion rules.

```{r}

```

2.  The following code will generate a warning. Explain why.

```{r}
as.integer(c("one", "two", "three"))
```

3.  Create a vector of a sequence of integers starting at 2, ending at 100, and increasing by 2. Assign the vector to an object called `evens`. Coerce the vector to be of type `integer`. Confirm that the vector is of type `integer`.

```{r}

```

4.  Create a vector of random numbers with a length equal to your vector in exercise 3. Use a seed with a value of 730 before creating your vector. Assign the vector to an object called `randoms`. Confirm the type of the vector.

```{r}

```

5.  Create a vector demonstrating which values in exercise 3 are greater than `0.75`. Assign the vector to an object called `logicals`. Confirm the type of the vector.

```{r}

```

6.  Create a data frame including the three vectors created in exercises 3 through 5. Assign it to an object following best practices for naming.

```{r}

```

7.  Create a new object which is the sum of `evens` and `randoms` all divided by 3. Demonstrate how to calculate basic summary statistics for this new object (mean, median, minimum, maximum, standard deviation, variance).

```{r}

```

8.  We discussed the idea that R is a "vectorized" language. Explain this concept. Why is it important?

9.  Run the `sessionInfo` function in a chunk.

```{r}

```

10. Follow the steps outlined in chapter 6-7 and 9-14 of *Happy Git and GitHub for the useR* in order to finish setting up git on your local machine and connecting your local machine to your GitHub account. Utilize the Slack channel `#help_git` if you run into any issues.
