---
title: "Week 01 Class Examples"
author: "Ryan Harrington"
date: "9/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
2 + 4
```

```{r}
1 - 4
```

+
-
*
/
()
^

```{r}
7 * 2
9 / 3
8 + 4 - 3
6 / (1 + 2)
(5 + 3) / 2 ^ 4
```

```{r}
1:10
```

name_of_the_object <- code

```{r}
top_ten <- 1:10
```

```{r, eval=FALSE}
snake_case
names.with.periods
CamelCase
```

```{r}
top_ten / 3
```

```{r}
top_ten - 3
top_ten ^ 2
```

Make an object called `top_ten_reversed`
Assign the numbers from to 10 to 1

```{r}
top_ten_reversed <- 10:1
```

```{r}
top_ten_reversed
```

```{r}
21:72
```

```{r}
10:1
```

```{r}
-3:-8
```

```{r}
TRUE
T

FALSE
F
```

>
<
>=
<=
==

```{r}
value <- 6 + 3
```

```{r}
value < 5
value > 3 ^ 2
value <= 10
value >= 10
```

```{r}
top_ten / value

top_ten < value

top_ten == value
```

This is text.

```{r}
# This is a comment
new_value <- 8 - 7

new_value              # this is a new value new_value
value                  # here's another value
```

```{r}
sqrt(value)

abs(-7)
```

vignette

mean
median
min
max
standard deviation
variance

```{r}
mean(top_ten)
median()
min()
max()
sd()
var()
```

```{r}
assignment_with_equal_sign = -3 ^ 2
```

```{r}
lost_numbers <- c(4, 8, 15, 16, 23, 42)
jennys_numbers <- c(8, 6, 7, 5, 3, 0, 9)

transcendental <- c(pi, 1.618, 2.713, sqrt(2), 4)

new_sequence <- c(1:10, jennys_numbers)

newer_sequence <- c(lost_numbers, jennys_numbers, new_value)
```

```{r}
all_sequences <- c(lost_numbers, jennys_numbers, transcendental)
```

From 2
To 50
By 2

```{r}
seq(from = 2, 
    to = 50, 
    by = 2)
```

```{r}
typeof(lost_numbers)

is.double(lost_numbers)
is.integer(lost_numbers)
is.numeric(lost_numbers)
```

Coercion

```{r}
lost_numbers <- as.integer(lost_numbers)

is.double(lost_numbers)
is.integer(lost_numbers)
is.numeric(lost_numbers)
```

```{r}
lost_numbers_again <- c(4L, 8L, 15L, 16L, 23L, 42L)

typeof(lost_numbers_again)
```

```{r}
set.seed(112)
random_logicals <- runif(n = 137, min = 0, max = 1) < 0.5
```
```{r}
typeof(random_logicals)
is.logical(random_logicals)
```

```{r}
random_logicals

as.integer(random_logicals)

sum(random_logicals)
```

```{r}

mean(random_logicals)

61 / 137
```


Character vs. String

```{r}
months_of_the_year <- c("January", "February", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December")
```

```{r}
typeof(months_of_the_year)
is.character(months_of_the_year)
```

logicals -> integers -> doubles -> character

```{r}
c(random_logicals, months_of_the_year)
```

```{r}
one_hundred_matrix <- matrix(1:100, nrow = 10, ncol = 10)
```

```{r}
months_df <- 
  data.frame(Months = months_of_the_year,
             Number = 1:12)
```

```{r}
data.frame(Months = months_of_the_year,
           Number = 1:11)
```

